Evolution plots

### 2016-02-18 scrap/evolution.Rmd
added nest density plots

```{R}
expf10_pop <- load_population("../data/exp_f10/")
expf15_pop <- load_population("../data/exp_f15/")
linf10_pop <- load_population("../data/lin_f10/")
population_plots <- function (what){
  print(pop_values(expf10_pop, what, paste("expf10_pop", what)))
  print(pop_values(expf15_pop, what, paste("expf15_pop", what)))
  print(pop_values(linf10_pop, what, paste("linf10_pop", what)))
}

population_plots("e_0")
population_plots("k")
population_plots("2 * radius * speed")

>>>>

```{R}
expf10_pop <- load_population("../data/exp_f10/")
expf15_pop <- load_population("../data/exp_f15/")
linf10_pop <- load_population("../data/lin_f10/")
population_plots <- function (y, x){
  print(pop_values(expf10_pop, x, y, paste("expf10_pop", y)))
  print(pop_values(expf15_pop, x, y, paste("expf15_pop", y)))
  print(pop_values(linf10_pop, x, y, paste("linf10_pop", y)))
}

population_plots("e_0", "patch_area")
population_plots("k", "patch_area")

```
These plots are against the log of the nest density ie log(nests / patch_area)
```{R}
population_plots("e_0", "log(N / patch_area)")
population_plots("k", "log(N / patch_area)")
